---
title: "Assignment 1"
---

# Assignment 1

My first assignment has two parts.

## (a)

## (b)

library(dslabs)
data("mtcars")

Created a custom_summary function and which is works to calculating mean, standard variance, max value in data set, min value in data set and median value.

```{r}
custom_summary <- function (carCustom)
{
    meanValue <- mean(carCustom)
    std <- sd(carCustom)
    maxValue <- max(carCustom)
    minValue <- min(carCustom)
    medianValue <- median(carCustom)
    customStatistics <- list(minValue,maxValue,meanValue,medianValue,std)
    return (customStatistics)
}
```

This stage custom_summary fuction calculated all values (mean, standard variance, max value in data set, min value in data set and median value) for each property of mtcars.

```{r}
customNames <- names(mtcars)
for (customIndex in 1:11){
    carCustom <- mtcars[,customIndex]
    customStatistics <- custom_summary(carCustom)
    print(customNames[customIndex])
    print(customStatistics)
}
```
The apply function and the custom_summary function were applied to all columns of the matrix.
```{r}
qq <- apply(mtcars,2,custom_summary)
print(qq)
```


## (c)

There is a Data Graph belongs to na_example data set.
```{r}
library(dslabs)
data("na_example")
plot(na_example, type = "l", main = "Data Graph", xlab = "Example Number", ylab = "Example Value")
```
You can see all the values of the na_example data set in the table below.
```{r}

print(na_example)
```

Number of elements which equal to NA in Data Set
```{r}

sum(is.na(na_example))
```

Convert NA's to 660


```{r}
convert_nas <- ifelse(is.na(na_example),660, na_example) 
```
You can see converted data below.
```{r}
print(convert_nas)
```

Total NA values at updated data set.
```{r}
sum(is.na(convert_nas))

```

Number of NA elements which are assigned to 660. 
```{r}
sumpro<-sum(convert_nas==660)
print(sumpro)
```