---
title: "Assignment 1"
---

# Assignment 1

```{r}
1 + 1
```

My first assignment has two parts.

## (a)

## (b)

library(dslabs)
data("mtcars")

custom_summary <- function (carCustom)
{
    meanValue <- mean(carCustom)
    std <- sd(carCustom)
    maxValue <- max(carCustom)
    minValue <- min(carCustom)
    medianValue <- median(carCustom)
    customStatistics <- list(minValue,maxValue,meanValue,medianValue,std)
    return (customStatistics)
}
customNames <- names(mtcars)
for (customIndex in 1:11){
    carCustom <- mtcars[,customIndex]
    customStatistics <- custom_summary(carCustom)
    print(customNames[customIndex])
    print(customStatistics)
}

qq <- apply(mtcars,2,custom_summary)
print(qq)

## (c)
```{r}
library(dslabs)
data("na_example")
plot(na_example, type = "l", main = "My Vector Plot", xlab = "Index", ylab = "Value")
```
```{r}

print(na_example)
```

Number of elements which equal to NA in Data Set
```{r}

sum(is.na(na_example))
```

Convert NA's to 660

You can see 
```{r}
convert_nas <- ifelse(is.na(na_example),660, na_example) 
```
```{r}
print(convert_nas)
```